\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}

### 2014-11-29 Proposal.tex
OMDoc part

%----------------------------------------------------------------------------------------
% Macros
%----------------------------------------------------------------------------------------
\newcommand{\sys}{Knowledge Presentation System\xspace}

@@

Semantic Web is aiming to change the former, whereas new, more visual presentation tools provide a solution to help provide presentations that are easier to process and thus will facilitate knowledge transfer. The work proposed here intends to bridge the gap and provide a tool for contextual visualization of information. It adapts some of the concepts of the semantic web on a smaller scale.

We want to go from merely displaying information to visualizing information to provide knowledge by displaying the network/context a piece of information is in. In this we will not try to semantically represent the meaning of the information that is shown but rather on showing the network, i.e. context the information is in.

@@

To exemplify this: Annie, a young student learning Spanish is watching her teacher give a presentation on how to form sentences. She wants to form the sentence 'I read books'. After struggling and looking up the word for reading she forms the sentence 'Yo leer libros'. For this Annie had to find the dependency on knowing the vocabulary words for 'I', 'read', and 'books'. However Annie made a mistake and did not know that the verb 'leer' needs to be conjugated appropriately. Her teacher tells her this. Now Annie has to try to find the information on how to conjugate verbs. This shows the dependencies of different pieces of information, i.e. the formulation of a sentence depends on knowledge of grammar and vocabulary. In an ideal presentation this information should have been linked to the current piece of information so that Annie could have directly looked it up instead of having to search for it.

After reading this contrived story, I leave the reader to think about examples in his or her own life where he or she would have appreciated having the context of the information he or she was looking at at the time. Many of these stories exist in real life and it is therefore important to provide this context to facilitate learning and knowledge transfer as a whole.

\ednote{-addresses fellow experts from your field (but not from your particular topic of research). }
\ednote{- Here you should technically connect to the main concepts from that field and give an outline of your project, stating the research/engineering question that you want to get answered by your project.}
\ednote{Why is this important for the world? How will this improve learning? ->More effective education. }
\ednote{(target size: 1 page)}
\ednote{http://rhizomik.net/html/~roberto/thesis/html/KnowledgeRepresentation.html}
\ednote{link}
% http://reader.eblib.com/(S(gkwt4h53aadjotp03mi25zsi))/Reader.aspx?p=655998&o=1706&u=tkyUhRRU8oBFV92xtGUdWNHfafo%3d&t=1416427415&h=AAEABAAD4041366D9CC8528AF618690B20349073&s=31025691&ut=5736&pg=1&r=img&c=-1&pat=n&cms=-1&sd=2

\section{Preliminaries}
To understand the problem of information that lacks context, this part will provide the necessary background information to allow us to derive a possible solution. While doing so it will demonstrate why this research is important and how it will improve the transfer of knowledge.

\ednote{ This part should make clear which question, exactly, you are pursuing, and why your project is relevant/interesting. This is the place to cite relevant literature. Where does your project extend the state of the art? what weaknesses in known approaches to you hope to overcome? If you have carried out preliminary experiments, describe them here.}

@@

\subsection{OMDoc}
(half a page)
\vspace*{8cm}
\subsection{Status of Information within Discourse}

In linguistics the concept of information packaging \cite{CambridgeGrammar:npentrel14} is known. Within this, one discriminates between \textit{familiar} and \textit{old} information. \textit{Familiar} information is shared by speaker and addressee, ie. common ground, whereas new information not. In addition one distinguishes information that is old or new with respect to the discourse or with respect to the addressee.\\

@@

These concepts can be adapted to the situation of teaching Mathematics or Computer Science to students in a class. In general the information that the speaker is sharing with the addressees/students is \textit{discourse-new}\ednote{call course-new?} and depend on  information that is \textit{discourse-old}. I would like to introduce the term \textit{discourse-ancient} which covers the situation where the addressee has difficulties following the speaker since the \textit{discourse-new} information depends on \textit{discourse-old} information that might be 'too old', i.e. ancient, to be easily remembered.\\

\subsection{Primitives}

@@

\ednote{evaluation criteria from lecture slides}
\newpage

\section{Work Plan}
\ednote {Add some speculation HOW}
\subsection{WP1: Understand API of Impress.js}
\ednote {should Impress.js go into the introduction/preliminaries? - I decided agains this as I haven't examined Impress.js enough yet.}
The first step to implementing a \sys is to understand the tool we want to represent the knowledge in later. Since Prezi at the current time does not have an API that would allow for the generation of a whole presentation without the editor, this research will employ another tool that is inspired by the idea behind Prezi. Bartek Szopka's \textbf{Impress.js} \cite{JSImpress:npentrel14} is an open-source presentation framework which is based on CSS3 transforms and transitions. \ednote{Impressionist and jimpress}\\

@@

\ednote{should users be able to reconstruct the original graph after a presentation? }

>>>>

\newenvironment{myfont}{\fontfamily{\sfdefault}\selectfont}{\par}

%----------------------------------------------------------------------------------------
% Macros
%----------------------------------------------------------------------------------------
\newcommand{\sys}{\textsc{Knowtation}\xspace}

@@

Semantic Web is aiming to change the former, whereas new, more visual presentation tools provide a solution to help provide presentations that are easier to process and thus will facilitate knowledge transfer. The work proposed here intends to bridge the gap and provide a tool for contextual visualization of information. It adapts some of the concepts of the semantic web on a smaller scale.\\

We want to go from merely displaying information to visualizing information to provide knowledge by displaying the network/context a piece of information is in. In this we will not try to semantically represent the meaning of the information that is shown but rather on showing the network, i.e. context the information is in.\\

@@

To exemplify this: Annie, a young student learning Math is watching her teacher give a presentation on how to use the Pythagorean theorem. She is given a triangle with sides a = 3 cm and b = 4 cm. Now she wants to use the theorem to calculate the length of side c. Annie already know how to calculate the square of a number and thus calculates that $c^2 = 25 \implies c = 5$. However Annie made a mistake and did not know what a right triangle is. Her teacher tells her that the question was a trick question and that the answer is wrong because the triangle she calculated this for is not a right triangle. Now Annie has to try to find out what a right triangle is. This shows the dependencies of different pieces of information, i.e. the Pythagorean theorem depends on knowledge of squares, lengths, area calculation, angles, and right angles. In an ideal presentation this information should have been linked to the current piece of information so that Annie could have directly looked it up instead of having to search for it.\\

After reading this contrived story, I leave the reader to think about examples in his or her own life where he or she would have appreciated having the context of the information he or she was looking at at the time. Many of these stories exist in real life and it is therefore important to provide this context to facilitate learning and knowledge transfer as a whole. \\

\ednote{-addresses fellow experts from your field (but not from your particular topic of research). }
\ednote{- Here you should technically connect to the main concepts from that field and give an outline of your project, stating the research/engineering question that you want to get answered by your project.}
\ednote{Why is this important for the world? How will this improve learning? ->More effective education. }
\ednote{(target size: 1 page)}
\ednote{http://rhizomik.net/html/~roberto/thesis/html/KnowledgeRepresentation.html}
\ednote{link}
% http://reader.eblib.com/(S(gkwt4h53aadjotp03mi25zsi))/Reader.aspx?p=655998&o=1706&u=tkyUhRRU8oBFV92xtGUdWNHfafo%3d&t=1416427415&h=AAEABAAD4041366D9CC8528AF618690B20349073&s=31025691&ut=5736&pg=1&r=img&c=-1&pat=n&cms=-1&sd=2
\ednote{use Knowledge Presentation System}
\ednote {KEEP - real question: does spatial narrative work together with inherent semantic closeness -cogn. question: how does the spatial narrative work - should we use the inherent semantic closeness
}
\section{Preliminaries}
To understand the problem of information that lacks context, this part will provide the necessary background information to allow us to derive a possible solution. While doing so it will demonstrate why this research is important and how it will improve the transfer of knowledge.\\

\ednote{This part should make clear which question, exactly, you are pursuing, and why your project is relevant/interesting. This is the place to cite relevant literature. Where does your project extend the state of the art? what weaknesses in known approaches to you hope to overcome? If you have carried out preliminary experiments, describe them here.}

@@

\subsection{OMDoc}
OMDoc (\textbf{O}pen \textbf{M}athematical \textbf{Doc}uments) \cite{Kohlhase:OMDoc1.2} is an XML-based system that provides a data model and a format for content markup for mathematical documents. As such it is a semi-formal domain ontology. An ontology provides the framework for creating a semantic structure. It formally describes concepts within a specified area. A semi-formal ontology \cite{Sheth:npentrel14} is an ontology where formality of semantics is not a given. The semi-formal ontology can consist of partial or incomplete knowledge. \\

If OMDoc was used in every part of mathematics (and related fields), we would have a repository of mathematical knowledge that could be processed in different ways. This is possible because OMDoc provides the framework to create and store mathematical objects such as definitions and concepts. The relations between different mathematical objects and the attributes of mathematical objects can be added through annotations. This elevates the net of separate pieces of information that are stored individually to a semantic representation and one step further to knowledge.\\

In \cite{LK:MathOntoAuthDoc09} it is stated that "documents consist of narrative and content layers". The content layers are the mathematical objects, i.e. the statements or theories. Narrative layers refer to the order the mathematical objects from content layers are presented. In the proposed research the mathematical knowledge will be processed and visualized in a way that enables students to learn more efficiently. Thus it will not only provide the information or provide a narrative but it will provide a more interactive approach to presentations and learning.\\

\subsection{Status of Information within Discourse}
\ednote{intersection of knowledge of student and teacher aka shared knowledge base (also called “content commons”)}
In linguistics the concept of information packaging \cite{CambridgeGrammar:npentrel14} is known. Within this, one discriminates between \textit{familiar} and \textit{old} information. \textit{Familiar} information is shared by speaker and addressee, ie. common ground, whereas new information not. In addition one distinguishes information that is old or new with respect to the discourse or with respect to the addressee.\\

@@

These concepts can be adapted to the situation of teaching Mathematics or Computer Science to students in a class. In general the information that the speaker is sharing with the addressees/students is \textit{discourse-new}\ednote{call course-new?} and depend on  information that is \textit{discourse-old}. I would like to introduce the term \textit{discourse-ancient} which covers the situation where the addressee has difficulties following the speaker since the \textit{discourse-new} information depends on \textit{discourse-old} information that might be 'too old', i.e. ancient, to be easily remembered.\\
\ednote {- reference old example from introduction -> and add onto it showing discourse-ancient.}
\subsection{Primitives}

@@

\ednote{evaluation criteria from lecture slides}
\ednote{add how to work packages. -> my first approach will be...}
\newpage

\section{Work Plan}
\ednote {Add some speculation HOW}
\subsection{WP1: Understand API of Impress.js}
\ednote {should Impress.js go into the introduction/preliminaries? - I decided against this as I haven't examined Impress.js enough yet.}
The first step to implementing a \sys \ednote{Is the font format ok?} is to understand the tool we want to represent the knowledge in later. Since Prezi at the current time does not have an API that would allow for the generation of a whole presentation without the editor, this research will employ another tool that is inspired by the idea behind Prezi. Bartek Szopka's \textbf{Impress.js} \cite{JSImpress:npentrel14} is an open-source presentation framework which is based on CSS3 transforms and transitions. \ednote{Impressionist and jimpress}\\

@@

\ednote {- work out concepts not a binding contract.}
\ednote{ 1. - 2. system goals -> kinda measurable}
\ednote{ 3.-5. cognitive goals -> exploring space of information systems}

\ednote{ make 2nd eval criteria last}
